\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2016-08-17 to-do.tex
added Becker & Murphy (1993), removed unnecessary lit from dynamic preferences'

\section{``Dynamic preferences''}
	\begin{itemize}
		\item James: need to be more precise about when $\ga$ is evaluated
			\begin{itemize}
				\item Skeptical of comparative-static style result: can I really compare governments with different $\ga$'s?
			\end{itemize}
		\item References from Krishna and Sadowski (2014) ECTA
				\begin{itemize}
					\item \sout{DILLENBERGER, D., J. S. LLERAS, P. SADOWSKI, AND N. TAKEOKA (2013): ``A Theory of Subjective Learning,'' Working Paper.}
						\begin{itemize}
							\item This is about figuring out the subjective learning structure by looking at a DM's preference for flexibility. Not directly relevant to my question b/c the information structure is objective.
						\end{itemize}
					\item GUL, F., AND W. PESENDORFER (2004): ``Self-Control and the Theory of Consumption,'' Econometrica, 72 (1), 119-158 (infinite horizon model)
					\item Gul and Pesendorfer's (2001) Econometrica is a two-period model. No dynamic inconsistency; derive temptation and desire for commitment in a model with dynamically consistent preferences.
					\item \sout{JONES, R. A., AND J. M. OSTROY (1984): ``Flexibility and Uncertainty,'' Review of Economic Studies, 51 (1), 13-32}
					\item (couldn't find) KOOPMANS, T. C. (1964): ``On the Flexibility of Future Preferences,'' in Human Judgments and Optimality, ed. by M. W. Shelly and G. L. Bryan. New York: Wiley.
					\item \sout{KREPS, D. M., AND E. L. PORTEUS (1978): ``Temporal Resolution of Uncertainty and Dynamic Choice Theory,'' Econometrica, 46 (1), 185-200.}
					\item Follow up on highlighted references in Kreps (1979): Strotz, which is about inconsistencies in discount function (non-exponential discounting).
					\item Promising: Hammond, Peter J., ``Changing Tastes and Coherent Dynamic Choice,'' The Review of Economic Studies, Vol. 43, No. 1 (Feb., 1976)
					\item Even better, especially advertising example: Becker, Gary. S. and George J. Stigler, ``De Gustibus Non Est Disputandum,'' The American Economic Review, Vol. 67, No. 2 (Mar., 1977), pp. 76-90
						\begin{itemize}
							\item I can make my argument almost exactly in analogy to this advertising example. My $\ga(e)$ function is like their $g(A)$.
							\item Check Kyle's Discussion paper on advertising to get context
						\end{itemize}
				\end{itemize}
			\item Giovanni: think of expost $\ga(e)$ as effort to elect/choose ex-post decision-maker
			\item At worst, I can use leg / exec split to deal with this criticism
			\item Kyle (???): advertising paper (???)
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
			\item Devashish: Utility fcn didn't change. Just got evaluated at a different point
				\begin{itemize}
					\item Preferences don't change. It's persuasion that affects decision-making. 2nd story: Giovanni's
					\item Find something in persuasion literature
				\end{itemize}
		\end{itemize}
	Bob: maybe gov't has some other reason for setting non-zero tariff that opens the door for lobbies. 2nd best remedy for market failure, etc.
	\begin{itemize}
			\item Maybe I should just get rid of tariff cap result altogether [me]
		\end{itemize}

>>>>

\section{``Dynamic preferences''}
	\begin{itemize}
		\item James: need to be more precise about when $\ga$ is evaluated
			\begin{itemize}
				\item Skeptical of comparative-static style result: can I really compare governments with different $\ga$'s?
			\end{itemize}
		\item References from Krishna and Sadowski (2014) ECTA
				\begin{itemize}
					\item Gul and Pesendorfer's (2001) Econometrica is a two-period model. No dynamic inconsistency; derive temptation and desire for commitment in a model with dynamically consistent preferences.
					\item Promising: Hammond, Peter J., ``Changing Tastes and Coherent Dynamic Choice,'' The Review of Economic Studies, Vol. 43, No. 1 (Feb., 1976)
					\item Even better, especially advertising example (credit Kyle): Becker, Gary. S. and George J. Stigler, ``De Gustibus Non Est Disputandum,'' The American Economic Review, Vol. 67, No. 2 (Mar., 1977), pp. 76-90
						\begin{itemize}
							\item I can make my argument almost exactly in analogy to this advertising example. My $\ga(e)$ function is like their $g(A)$.
						\end{itemize}
					\item Simpler: Becker, G. S. and K. M. Murphy (1993), “A Simple Theory of Advertising as a Good or Bad,” Quarterly Journal of Economics, 942-64.
				\end{itemize}
			\item At worst, I can use leg / exec split to deal with this criticism
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
			\item Devashish: Utility fcn didn't change. Just got evaluated at a different point
				\begin{itemize}
					\item Preferences don't change. It's persuasion that affects decision-making. 2nd story: Giovanni's ``expost $\ga(e)$ as effort to elect/choose ex-post decision-maker''
				\end{itemize}
		\end{itemize}
	Bob: maybe gov't has some other reason for setting non-zero tariff that opens the door for lobbies. 2nd best remedy for market failure, etc.
